Experiences with long-term monitoring of a large-scale distributed and heterogenous cyberinfrastructure

### 2013-10-02 pubs/papers/inca-analysis/Inca-anaylsis.tex
Updated text.
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@15331 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

\documentclass{IEEEtran}
\usepackage{subfigure,url}

@@

\section{Introduction} (0.5 page)

\section{FutureGrid Overview} (1 page)
Add description of load -- vm count, hrs. etc.

@@

\section{Inca Architecture} (0.5 page)

@@

\section{Use cases} (0.5 pages)

\section{Test suite classes} (0.5 pages)

\section{Analysis results} (4 pages)
Description of the methodology -- how data was filtered and interpreted.

\subsection{SSH data}
\subsubsection{Failure Classifiation:} What types of failures do we see?
\subsubsection{Failures distribution:} Are failures independent or related?
\subsubsection{predictability} Is this system system predictable in terms of resource availability or failures.
\subsection{site-level}: How do different sites compare in terms of reliability.

@@

\subsection{cloud-stats}
\subsection{hpc-stats:} benchmarks, version numbers.

@@

\section{Related Work} (0.5 page)

\section{Future Work} (0.25 page)

\section{Conclusion} (0.25 page)

>>>>

\documentclass{IEEEtran}
\usepackage{graphicx,subfigure,url, amsmath}

@@

\section{Introduction} (0.5 page) (Sameer and Shava)

\section{FutureGrid Overview} (0.5 page) (Shava)

Add description of load -- vm count, hrs. etc.

@@

\section{Inca Architecture} (0.5 page) (Shava)

@@

\section{Monitoring data analysis} (3 - 4 pages)

\subsection{Test suite description} (2 pages, 0.5 page/class) (Shava)
Description of the methodology -- how data was filtered and interpreted.

\subsection{Results} (Sameer)

\subsection{SSH data}
\subsubsection{Failure Classification:} What types of failures do we see?

\begin{figure*}
\begin{center}
\includegraphics[scale=0.60]{figs/fg-failure-counts}
\caption{Failure Classification}
\label{fig:fg-failure-counts}
\end{center}
\end{figure*}

\subsection{site-level}: How do different sites compare in terms of reliability.

%$\begin{equation} \label{eq:MTBF}
$ MTBF$ =  $\Sigma$ (start of downtime - start of uptime) $/$ (number of failures)
% \end{equation}

\begin{figure*}
\centering
\mbox{
\subfigure[MTBF for all FutureGrid sites ]{
   \includegraphics[scale =0.70] {figs/MTBF}
   \label{fig:subfig1}
 }\quad

 \subfigure[Failure counts for all FugureGrid sites]{
   \includegraphics[scale =0.70] {figs/site-level-failure-count}
   \label{fig:subfig2}
 }
}
\centering
\label{myfigure}
\caption{Android software stack and its comparison with Linux}
\end{figure*}

\subsubsection{Failures distribution:} Are failures independent or related?
\subsubsection{predictability} Is this system system predictable in terms of resource availability or failures.

\subsection{cloud-stats}

\begin{tabular}{| l | c | c | c | c | }
 \hline
Nimbus & tacc-alamo  & uc-hotel & ucsd-sierra  & ufl-foxtrot   \\
  \hline
clientStatus & 98\% & 96\% &  81\% &  80\% \\  \hline
create-publicvm & 93\%& 89\% &  91\% & 58\% \\  \hline
storage & 100\% & 97\% & 98\% &  99\% \\  \hline

\end{tabular}
\caption{Nimbus: Reliability across FutureGrid machines}
 \label{tab:nimbus-fg-reliability}

\begin{tabular}{| l | c | c | c | c | }
 \hline
Eucalyptus & iu-india  & ucsd-sierra    \\
  \hline
clientStatus & 96\% & 93\%  \\  \hline
create-publicvm & 77\%& 56\%  \\  \hline
storage & 100\% & 97\%   \\  \hline

\end{tabular}
\caption{Eucalyptus: Reliability across FutureGrid machines}
 \label{tab:eucalyptus-fg-reliability} 
\end{table*}

@@

\begin{tabular}{| l | c | c | c | c | }
 \hline
Openstack & iu-india      \\
  \hline
clientStatus & 97\%   \\  \hline
create-publicvm & 71\%  \\  \hline
storage & 80\%  \\  \hline

\end{tabular}
\caption{Openstack: Reliability across FutureGrid machines}
 \label{tab:openstack-fg-reliability}

\subsection{hpc-stats:} benchmarks, version numbers.

\begin{tabular}{| l | c | c | c | c | c | c | c | }
 \hline
HPC jobs & iu-bravo & iu-delta & iu-india  & iu-xray  & tacc-alamo & uc-hotel & ucsd-sierra \\
  \hline
batch-testjob & & & 88\% & 97\% &   77\% &  100 & 99\% \% \\  \hline
batch-testjob\_to\_bravo & 99\% & & & & & & \\  \hline
batch-testjob\_to\_delta &  & 95\% & & & & & \\  \hline
CUDA-testjob\_to\_delta &  & 95\% & & & & & \\  \hline
myhadoop &  & & 54\% & & 59\% & 89\% & 47\%  \\  \hline

\end{tabular}
\caption{HPC jobs: Reliability across FutureGrid machines}
 \label{tab:hpc-fg-reliability}

\begin{tabular}{| l | c | c | c | c | }
 \hline
HPCC jobs & iu-india  & iu-xray & ucsd-sierra    \\
  \hline
hpcc8 & 99\% & 97\% & 72\% \\  \hline
hpcc16 & 99\% & 96\% & \\  \hline
hpcc32 &  & 95\% &   \\  \hline
hpcc64 & 97\% & 96\% &  \\  \hline
hpcc128 & 93\% & 93\% &   \\  \hline
hpcc256 & 79\% & 71\% &   \\  \hline
hpcc512 & & 93\% &   \\  \hline
hpcc672 & & 99\%  &  \\  \hline

\end{tabular}
\caption{HPCC jobs: Reliability across FutureGrid machines}
 \label{tab:hpcc-fg-reliability} 
\end{table*}

@@

\section{Lessons Learned / Best Practices} (1 page) (Shava and Sameer)

\section{Related Work} (0.5 page) (Shava and Sameer)

\section{Future Work} (0.25 page) (Shava and Sameer)

\section{Conclusion} (0.25 page) (Shava and Sameer)
